How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-28 tse-paper/content.tex
addressing some todos and writing longer conclusion

When a build or one of its steps fails, developers typically scavenge
the logs for information related to the source of the error.
This
manual activity is tedious and prone to
error~\cite{santolucito2018statically}.
As a single build log can be
over 50 megabytes large~\cite{beller2017oops}, finding the small chunk
of information in it which is linked to the actual error, is akin to
searching for a needle in a haystack.
The large numbers of unrelated, but amibguous warnings that many build
logs regularly contain, further compounds this problem.
In addition to helping
understand and fix build failures, the information richness of build
logs enables a plethora of other applications: with the help of build
logs, we can better understand and categorize CI failures and compile
errors~\cite{islam2017insights,seo2014programmers}, differentiate
testing practices~\cite{orellana2017differences,vassallo2017a-tale},
train classifiers to do ``predictive CI'' on the build or test outcome
and
duration~\cite{ni2017cost,bisong2017built,haghighatkhah2018test,machalica2019predictive},
or investigate the role of automated static analysis tools (ASATs,
\cite{beller2016analyzing}) in CI
builds~\cite{zampetti2017open}.

@@

To answer this question, we start our investigation---pictured in
\Cref{fig:overview}---with an
extensive literature study (step 1).
The literature
survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
searching for keywords, or performing natural language processing.
However, there is currently no guidance on when to use which of these
approaches.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
the few available implementations are all based on either a custom parser
or regular expressions.
These two approaches in particular are problematic, as their creation
and maintenane is manual and expensive, does not generalize across build
logs from different build environments, and is, as the experience of
TravisTorrent has shown, prone to error.
In fact, some even ``strongly discourage'' the creation of such
bespoke parsers~\cite{urli2018design}.
In summary, the outcome of our literature survey shows the need for a new
generation of automated techniques to analyze build logs, which are
documented in detail and which are openly available, together with
guidance on when to use which tool.

@@

% TODO caro: maybe convert this into a proper ordered list?
To fill this gap, we adapted and implemented three novel, prototypical
implementations to
automatically analyze build logs.
The ideas behind the implementations are based on promising approaches
adopted from other research fields and automatic build log analysis
techniques:
a technique 1) able to automatically synthesize regular expressions,
called \emph{Program Synthesis by Example (PBE)}, 2) based on information
retrieval, using \emph{Common Text Similarity (CTS)}  and 3)
inspired by the manual adhoc-search for key parts in the log, employing
\emph{Keyword Search (KWS)}.
These three approaches---regular expressions, text similarity,
keyword search---
have different strengths and weaknesses.
As a consequence,
in the second research question we ask:

@@

To answer this question, as a third step,
we conduct an empirical study assessing the performance
of these chunk retrieval techniques in
real-world projects under a variety of conditions.
Our study is based on the \emph{LogChunks} data
set~\cite{brandt2020logchunks}, which encompasses 797 build logs from
80 popular open-source projects and a broad range of different
build tools and programming languages.
Our results show that there is no technique that in general outperforms
the others.
However,
% TODO Caro: 1-2 sentences about results, inclduing some accuracy measures

@@

% TODO something like overall, we argue that our implementations and their
% weaknesses stand prototypical for the techniques and tried to limit
% idiosyncrazies as much as possible (give example)

@@

\section{Conclusion}
\label{sec:conclusion-fw}
% TODO CARO conclusion should be a bit longer and a little bit more in
% detail.
 TODO Mention general accuracy measures (techniques performed
up to in F1 score, which is x times better than RLR)
The goal of this paper is to support practitioners and researchers in
their decision on how to analyze build logs.
To this end, we first
conducted a systematic mapping study to map out the available build
log analysis techniques.
We then
implemented three promising chunk retrieval techniques and compared
their performance on the \emph{LogChunks} data set.
Our results show
that the structural representation of the targeted information in the
build logs is the main factor to consider when choosing a suitable
technique.
Secondary factors are the desired confidence in recall and
precision of the produced output and whether precision or recall is
more important for the task at hand.

Finally, we gave an
outline to guide future research efforts in the area of build log
analysis.
Important themes are
% TODO Caro complete :-)

>>>>

When a build or one of its steps fails, developers typically scavenge
the logs for information related to the source of the error.
This
manual activity is tedious and prone to
error~\cite{santolucito2018statically}.
As a single build log can be
over 50 megabytes large~\cite{beller2017oops}, finding the small chunk
of information in it which is linked to the actual error, is akin to
searching for a needle in a haystack.
The large numbers of unrelated, but ambiguous warnings that many build
logs regularly contain, further compounds this problem.
In addition to helping
understand and fix build failures, the information richness of build
logs enables a plethora of other applications: with the help of build
logs, we can better understand and categorize CI failures and compile
errors~\cite{islam2017insights,seo2014programmers}, differentiate
testing practices~\cite{orellana2017differences,vassallo2017a-tale},
train classifiers to do ``predictive CI'' on the build or test outcome
and
duration~\cite{ni2017cost,bisong2017built,haghighatkhah2018test,
machalica2019predictive},
or investigate the role of automated static analysis tools (ASATs,
\cite{beller2016analyzing}) in CI
builds~\cite{zampetti2017open}.

@@

To answer this question, we start our investigation---pictured in
\Cref{fig:overview}---with an
extensive literature study (step 1).
The literature
survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
searching for keywords, or performing natural language processing.
However, there is currently no guidance on when to use which of these
approaches.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
the few available implementations are all based on either a custom parser
or regular expressions.
These two approaches in particular are problematic, as their creation
and maintenance is manual and expensive, does not generalize across build
logs from different build environments, and is, as the experience of
TravisTorrent has shown, prone to error.
In fact, some even ``strongly discourage'' the creation of such
bespoke parsers~\cite{urli2018design}.
In summary, the outcome of our literature survey shows the need for a new
generation of automated techniques to analyze build logs, which are
documented in detail and which are openly available, together with
guidance on when to use which tool.

@@

% M: maybe convert this into a proper ordered list?
% TODO Moritz: not sure what you mean here ?
% I agree that the non-itemized looks better than before
To fill this gap, we adapted and implemented three novel, prototypical
implementations to
automatically analyze build logs.
The ideas behind the implementations are based on promising approaches
adopted from other research fields and automatic build log analysis
techniques:
a technique 1) able to automatically synthesize regular expressions,
called \emph{Program Synthesis by Example (PBE)}, 2) based on information
retrieval, using \emph{Common Text Similarity (CTS)}  and 3)
inspired by the manual adhoc-search for key parts in the log, employing
\emph{Keyword Search (KWS)}.
These three approaches---regular expressions, text similarity,
keyword search---
have different strengths and weaknesses.
As a consequence,
in the second research question we ask:

@@

To answer this question, as a third step,
we conduct an empirical study assessing the performance
of these chunk retrieval techniques in
real-world projects under a variety of conditions.
Our study is based on the \emph{LogChunks} data
set~\cite{brandt2020logchunks}, which encompasses 797 build logs from
80 popular open-source projects and a broad range of different
build tools and programming languages.
Our results show that there is no technique that in general outperforms
the others.
PBE has the best average precision of 95\%, while KWS has the largest
recall with 70\% on average.
However, CTS shows the best F$_{1}$-score
of 51\% and all of the three techniques
clearly outperform a random baseline.

@@

% kinda uncreative..
not sure what another example would be?
% not sure if this adds much on top of the sentences further up
Overall, we believe our implementations and their weaknesses stand
prototypical for the techniques.
We tried to limit idiosyncrasies as much as possible, by choosing
standard approaches and configurations.

@@

\section{Conclusion}
\label{sec:conclusion-fw}

The goal of this paper is to support practitioners and researchers in
their decision on how to analyze build logs.
To this end, we first
conducted a systematic mapping study to map out the available build
log analysis techniques.
We saw that while build log analysis is widely used, it is often
a side-part of the article and implementations are rarely reused.
This shows the need for a new generation of generic and automated
build log analysis techniques that need little effort to set up.
Based
on common approaches we saw during the literature survey,
we implemented three promising techniques to retrieve specific
substrings (chunks) from build logs:
PBE synthesizes regular expression programs based on examples of logs
and corresponding chunks, CTS leverages a common text similarity
measure to retrieve those lines which are most similar to example
chunks, and KWS finds the targeted parts of a build log by searching
for identifying keywords.
We evaluated the performance of these chunk retrieval techniques on the
\emph{LogChunks} data set and saw varying results.
CTS had the highest average F$_{1}$-score with 51\%, while the other
techniques showed higher average scores for precision (95\%, PBE)
and recall (70\%, KWS).
To guide researchers and developers on which technique to use for their
we summarized our results in a decision tree.
We found
that the structural representation of the targeted information in the
build logs is the main factor a user should consider when they
choose a suitable
technique.
Secondary factors are the desired confidence in recall and
precision of the produced output and whether precision or recall is
more important for the task at hand.
Finally, we gave an
outline to guide future research efforts in the area of build log
analysis.
Important themes are a systematic investigation of industry approaches,
benchmarks of existing build log analysis approaches and further
refinement of the chunk retrieval techniques we proposed.
